AA Distributed Software Development Methodology

### 2013-02-18 paper.tex
bombei inicio results and discussion

\subsection{Validation}

Each AA session must be validated by another developer, it means that
all reports are read by someone that will consider then valid or not
and will even write commentaries about the specific session. The
developer in charge of validating a session is decided randomly by the
AA Web server, which send an email to the chosen developer with an
URL to a validation interface.

@@

The easy and effective management of teams working on GSD is the main
purpose of the AA methodology. We applied this methodology to a group
of 9 developers in July of 2011 on what we called Lab
Macambira~\footnote{LabMacambira.sf.net:
  \url{http://labmacambira.sf.net}}. The main objective of the team
was to work on different free software projects, contributing directly
to their development, sending bug corrections or proposing new
features on their source code.

All the team members had different levels of knowledge on software
development as part of large and distributed free software projects
like Scilab or Mozilla. In this way, one month of training was
conducted by two experienced developers, teaching the basics of use of
development support tools like bugtrackers, programming languages and
version control systems. After this period, a challenge was proposed
for the new developers: send a bug correction or a new feature to a
large free software project and you will work with us, you will be a
``Macambira'' developer. Table~\ref{tabela:contribuicoes} summarizes
the contributions of each ``Macambira'' to free software projects.

>>>>

\subsection{Peer Validation}

In order to prevent spamming and to improve the overall quality of AA reports,
each AA session must be validated by another developer. More specifically,
all reports are read by someone that will mark them as `valid' or `invalid'
and may optionally write commentaries about the specific session and quality of
micrologs. The developer in charge of validating any given session is randomly assigned 
by the AA Web server, which sends an email to the chosen developer with an URL to
a validation interface.

@@

Easy and effective GSD team management is the main
purpose of the AA methodology. We applied the proposed methodology to a group
of 9 developers in July of 2011 on what we called Lab
Macambira~\footnote{LabMacambira.sf.net: \url{http://labmacambira.sf.net}}. The
main objective of the team was to work on an array of strategic free software
projects in the broad audiovisual and web categories,
contributing directly to their development, submitting bug patches or
committing new features to their source code.

The team members had different levels of experience on software
development for large and distributed free software projects
like Scilab or Mozilla. In this way, one month of training was
conducted by two experienced developers, teaching the basics of use of
development support tools like bugtrackers, programming languages,
version control systems, and build systems. After this period, a starter project
was proposed for new developers, namely to have an accepted patch or commit to
the official repository for a large and widely used free software app.
Developers passing the starter project would be deemed `initiated' and be
called a `Macambira' developer.  Table~\ref{tabela:contribuicoes} summarizes the
effective accepted contributions of each successfully initiated developer to
free software projects in 2011.
